\begin{thebibliography}{9}

\bibitem{computinghistory}
Computing History Web Page
\\\texttt{\url{https://www.livescience.com/20718-computer-history.html}}

\bibitem{cloudcomputing}
A.M. Middleton.
\textit{Data-Intensive Technologies for Cloud Computing}. 
Handbook of Cloud Computing. Springer, 2010.

\bibitem{interactiveprocessing} 
Interactive and Batch Processing
\\\texttt{\url{https://www2.le.ac.uk/offices/itservices/ithelp/services/hpc/run-computation/interactive-or-batch}}

\bibitem{streamprocessing} 
Ververica Web Page
\\\texttt{\url{https://www.ververica.com/what-is-stream-processing}}

\bibitem{gdprwebpage} 
General Data Protection Regulation Web Page
\\\texttt{\url{https://gdpr-info.eu/}}

\bibitem{privacypoliciesarticle} 
Michele Guerriero, Damian Andrew Tamburri, Elisabetta Di Nitto.
\textit{Defining, Enforcing and Checking Privacy Policies In Data-Intensive Applications}. 
13th International Symposium on Software Engineering for Adaptive and Self-Managing Systems, 2018.

\bibitem{parallelcomputing} 
D.B. Skillicorn and D. Talia.
\textit{Models and languages for parallel computation}. 
ACM Computing Surveys, Vol. 30, No. 2, 1998, pp. 123-169.

\bibitem{computing21} 
I. Gorton, P. Greenfield, A. Szalay and R. Williams.
\textit{Computing in the 21st Century}. 
IEEE Computer, Vol. 41, No. 4, 2008, pp. 30-32.

\bibitem{dataintensivecomputing} 
W.E. Johnston.
\textit{High-Speed, Wide Area, Data Intensive Computing: A Ten Year Retrospective}. 
IEEE Computer Society, 1998.

\bibitem{dataintensivecomputingIEEE} 
M. Gokhale, J. Cohen, A. Yoo and W.M. Miller.
\textit{IEEE: Hardware Technologies for High-Performance Data-Intensive Computing}. 
IEEE Computer, Vol. 41, No. 4, 2008, pp. 60-68.

\bibitem{terascalechallenge} 
D. Ravichandran, P. Pantel and E. Hovy.
\textit{The terascale challenge}. 
Proceedings of the KDD Workshop on Mining for and from the Semantic Web, 2004.

\bibitem{distributedcomputing} 
J. Gray.
\textit{Distributed Computing Economics}. 
ACM Queue, Vol. 6, No. 3, 2008, pp. 63-68.

\bibitem{scalablecomputing} 
R.E. Bryant.
\textit{Data Intensive Scalable Computing}. 
2008.

\bibitem{hadoopwebsite} 
Hadoop Tutorial
\\\texttt{\url{https://data-flair.training/blogs/hadoop-tutorial/}}

\bibitem{sparkwebsite} 
Spark Tutorial
\\\texttt{\url{https://data-flair.training/blogs/spark-tutorial/}}

\bibitem{flinkwebsite}
Apache Flink Tutorial
\\\texttt{\url{https://data-flair.training/blogs/apache-flink-tutorial/}}

\bibitem{dataprivacy}
Data Privacy Blog
\\\texttt{\url{https://www.varonis.com/blog/data-privacy/}}

\bibitem{privpoldef}
Privacy Policy Definition
\\\texttt{\url{https://www.techopedia.com/definition/23679/privacy-policy}}

\bibitem{computersecurityslides} 
Ken Thompson.
\textit{Reflections on Trusting Trust}. 
Communications of the ACM, 1984.

\bibitem{hipaablog}
Health Insurance Portability and Accountability Act Blog
\\\texttt{\url{https://www.varonis.com/blog/hipaa-compliance/}}

\bibitem{glbablog}
Gramm-Leach-Bliley Act Blog
\\\texttt{\url{https://www.varonis.com/blog/we-need-to-talk-about-gramm-leach-bliley-glb-the-safeguards-rule-will-be-changing/}}

\bibitem{ccpablog}
California Consumer Privacy Act Blog
\\\texttt{\url{https://www.varonis.com/blog/california-consumer-privacy-act-ccpa/}}

\bibitem{XACMLlanguage} 
Carroline Dewi Puspa Kencana Ramli, Hanne Riis Nielson, Flemming Nielson.
\textit{The logic of XACML}.

\bibitem{XACMLforAuthentication} 
Markus Lorch, Seth Proctor, Rebekah Lepro, Dennis Kafura, Sumit Shah.
\textit{First Experiences Using XACML for Access Control in Distributed Systems}.

\bibitem{modelwebsite} 
Modeling Tutorial
\\\texttt{\url{https://www.transentis.com/methods-techniques/models-and-metamodels/}}

\bibitem{metamodelwebsite} 
Dimitris Karagiannis, Harald Kühn
% http://www.dke.univie.ac.at/mmp/FullVersion_MMP_DexaECWeb2002.pdf
\textit{Metamodeling Platforms}
Springer-Verlag, 2002

\bibitem{umlwebsite} 
Unified Modeling Language Tutorial
\\\texttt{\url{https://www.visual-paradigm.com/guide/uml-unified-modeling-language/what-is-uml/}}

\bibitem{yeastfermentation} 
Temperature Control For Yeast Fermentation
\\\texttt{\url{http://www.theartisan.net/temperature\_control\_baking\_1.htm}}


\end{thebibliography}
